\documentclass[11pt]{article}
\include{macros}
\usepackage{hyperref}
\newcommand{\thisdocument}{RRF: Literature Citations}

\begin{document}

\noindent{}This a selection of the PI's recent publications that are
relevant to this proposal.  They are on Sage or use Sage extensively
for applications to education and research in number theory.


\begin{enumerate}\setlength{\itemsep}{0ex}

\item \emph{A Database Of Elliptic Curves Over $\mathbf{Q}(\sqrt{5})$ -- First
  Report (16 pages)}, with J. Bober, A. Deines, A. Klages-Mundt,
  B. LeVeque, R. A. Ohana, A. Rabindranath, P. Sharaba, 2012, to
  appear in ANTS X. (Used Sage extensively and involved many
  students.) \url{http://wstein.org/papers/sqrt5/}

\item \emph{Sage: Creating a Viable Free Open Source Alternative to
  Magma, Maple, Mathematica, and MATLAB} (9 pages), Foundations of
  Computational Mathematics 2011 proceedings (the PI was a plenary
  speaker). \url{http://wstein.org/papers/focm11/}

\item \emph{The Sage Project: Unifying Free Mathematical Software to
  Create a Viable Alternative to Magma, Maple, Mathematica and Matlab}
  (16 pages), with B. Erocal, 2010, for the PI's plenary talk at
  the 2010 International Congress of Mathematical Software in Japan.
\url{http://wstein.org/papers/icms/icms_2010.pdf}

\item \emph{Fast Computation of Hermite Normal Forms of Random Integer Matrices}
(9 pages), 2010, J. Number Theory.  (Paper that came out of implementing core linear
 algebra algorithms in Sage.) \url{http://wstein.org/papers/hnf/}

 \item {\ptitle Verification of the Birch and Swinnerton-Dyer
   Conjecture for Specific Elliptic Curves}, with G. Grigorov, A.
   Jorza, S. Patrikis, and C. Patrascu (26 pages), 2009, 
   Mathematics of Computation.   (Used Sage greatly; involved many students.)
\url{http://wstein.org/papers/bsdalg/}

\item \emph{Elementary Number Theory: Primes, Congruences, and Secrets}
 (book), 2008, published by Springer-Verlag. (Extensive Sage code included.)
\url{http://wstein.org/ent/}

 \item \emph{Explicitly {C}omputing {M}odular {F}orms} (284 page),
 Graduate Studies in Mathematics (AMS), 
 2007, with an appendix by Paul Gunnells. (Extensive Sage code included.)
\url{http://wstein.org/books/modform/}

 \item \emph{Opinion: Open Source Mathematical Software} (2007), with
   D. Joyner, Notices of the AMS, {\bf 54}, no. 10.
\url{http://www.ams.org/notices/200710/}



\end{enumerate}




\end{document}
