\documentclass[11pt]{article}
\include{macros}
\newcommand{\thisdocument}{RRF: Biographical Sketch}

\begin{document}
%\maketitle

\head{Professional Preparation}%
\begin{center}
\begin{tabular}{lll}
  % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
\mbox{}\hspace{4.2ex}&   Northern Arizona University\hspace{1.03in}\mbox{}& Mathematics, B.S. 1994 \\
&  University of California at \textbf{Berkeley} & Mathematics, Ph.D. 2000 \\
&  \textbf{Harvard University} & NSF postdoc, 2000--2004 \\
\end{tabular}
\end{center}

\head{Appointments}
\begin{itemize}\setlength{\itemsep}{0ex}
\item Associate Professor of Mathematics (with tenure),
University of Washington, September 2006--present.
\item Associate Professor of Mathematics (with tenure),
UC San Diego, July 2005--June 2006.
\item Benjamin Peirce Assistant  Professor  of Mathematics, 
Harvard University, July 2001--May 2005.
\item NSF Postdoctoral Research Fellowship 
under Barry Mazur at Harvard University, August 2000--May 2004.
\item Clay Mathematics Institute Liftoff Fellow, Summer 2000.
\end{itemize}


\head{Synergistic Activities}
\begin{itemize}\setlength{\itemsep}{0ex}

\item {\bf Research Tools:} Director of the Sage project, which has
  produced over 300,000 lines of new code and an integrated
  distribution of about 5,000,000 lines of code.  Author of the
  modular forms, modular symbols and modular abelian varieties parts
  of the Magma computer algebra system.%

\item {\bf Outside Service:} IDA/CCR consultant.  Also, Defense
  Science Study Group member 2002--2003: DSSG is a DARPA funded
  program administered by the Institute for Defense Analysis; paper on
  GPS vulnerabilities.
\item {\bf Outreach:} SIMUW 2006, 2007, 2008 (summer UW high school
  math program); Canada/USA MathCamp mentor (2002).
\end{itemize}

\head{Other Affiliations}
\newcommand{\hl}[1]{#1}%
\begin{itemize}\setlength{\itemsep}{0ex}
\item \textbf{Graduate and Postdoctoral Advisors:}
\begin{itemize}
\item {\bf Ph.D. adviser:} Hendrik Lenstra, University of Leiden,
Netherlands.%
\item {\bf NSF Postdoctoral adviser:} Barry Mazur, Harvard
University.
\end{itemize}
\item \textbf{Thesis Students:}  3 Ph.D. students:  
Robert Miller and Robert Bradshaw at Univ. of Washington.
Co-advised Ifti Burhanuddin's Ph.D. in Computer Science at Univ. of
Southern California. Advised eight undergraduate senior theses at
Harvard, and two at UW. 
\end{itemize}


\end{document}
