\documentclass[11pt]{article}
\include{macros}
\newcommand{\thisdocument}{RRF: Other Research Support}

% Other research support. List sources, dates, amounts, and titles of
% all research awards for which you were the PI during the past three
% years, as well as pending proposals. State the relationship of each
% project to the current proposal, if any. Provide this information
% for the PI and each co-PI. Junior faculty should also list the total
% amount and remaining balance of their start-up package. (If you have
% no other research support to report, simply include a statement to
% this effect.)

% SINCE Sept 2009

\begin{document}
\mbox{}

This is a list of the sources, dates, amounts, titles and relevance of
research awards and contracts for which Stein was the PI during the
past three years.

\begin{itemize}\setlength{\itemsep}{0ex}

\item NSF, 07/01/12 - 06/30/15, \$224,557, {\em Explicit Approaches to Elliptic Curves, Modular Forms, and Modular Abelian Varieties}; fundamental research in number theory unrelated to current proposal.
\item NSF, 06/01/12 - 05/31/15, \$97,114, {\em Collaborative Research: Sage-combinat: Developing and Sharing Open Source Software for Algebraic Combinatorics}; fundamental research in combinatorics unrelated to current proposal.
\item NSF, 09/01/10--08/31/13, \$62,706, {\em
  Collaborative Research (AIM): UTMOST: Undergraduate Teaching in
  Mathematics with Open Software and Textbooks}; provides summer support during which I did work on Salvus, and provides valuable opportunities to interact with potential customers.
\item NSF, 09/15/10--08/31/13, \$140,000, {\em Sage: Unifying Mathematical Software for Scientists, Engineers and Mathematicians}; supports workshops on Sage, which is one of the software components that is relevant to the current proposal.
\item US Department of Defense, 09/01/10 - 09/20/13, \$209,664, {\em
  SAGE: Mathematical Software Development}; supports bug fixing workshops on Sage, but is otherwise unrelated to the current proposal.
\item NSF, 2008--2012, \$1,219,078, {\em FRG: L-functions and Modular Forms}; fundamental number theory research unrelated to the current proposal.
\item NSF, 2007--2010, \$144,543, 
  {\em The Sage Postdoc} (a 3-year postdoc at UW); supported some development work on Sage.



\end{itemize}




\end{document}
